Containers and R: the Rockerverse and beyond

### 2019-08-19 manuscript.Rmd
One sentance per line

_Bioconductor_ is a free, open source and open development project for
the analysis and comprehension of genomic data [1]. The project
consists of 1741 R software packages as of August 15th 2019, as well
as packages containing annotation or experiment data. _Bioconductor_
has a semiannual release cycle, each release is associated with a
particular version of R. Docker images allow availability of current
and past versions of _Bioconductor_ for convenience and
reproducibility.

@@

Bioconductor's _bioc_docker_ software works using a templating engine
based in ruby, has a source directory `src` and an output directory
`out`.[*] This takes away in large part the repeated handcrafting of
each Dockerfile produced by Bioconductor at each release cycle. Edits
to the Dockerfile need to be made in the source directory, based on a
config file, the output directory is populated with the appropriate
Dockerfile for each specific to the various areas of research. A
recent systematic "audit" of our docker images following best
practices (as issued by the Docker website) led to a reduction in the
number of layers and also size of the overall images being produced by
Bioconductor. Some of the optimizations include removing cache,
cleaning up after each layer produced by a `RUN` statement, and most
importantly, not re-installing any dependencies already provided by
rocker.

>>>>

_Bioconductor_ is a free, open source and open development project for the analysis and comprehension of genomic data [1].
The project consists of 1741 R software packages as of August 15th 2019, as well as packages containing annotation or experiment data.
_Bioconductor_has a semiannual release cycle, each release is associated with a particular version of R.
Docker images allow availability of current and past versions of _Bioconductor_ for convenience and reproducibility.

@@

Bioconductor's _bioc_docker_ software works using a templating engine based in ruby, has a source directory `src` and an output directory `out`[*].
This takes away in large part the repeated handcrafting of each Dockerfile produced by Bioconductor at each release cycle.
Edits to the Dockerfile need to be made in the source directory, based on a config file, the output directory is populated with the appropriate Dockerfile for each specific to the various areas of research.
A recent systematic "audit" of our docker images following best practices (as issued by the Docker website) led to a reduction in the number of layers and also size of the overall images being produced by Bioconductor.
Some of the optimizations include removing cache, cleaning up after each layer produced by a `RUN` statement, and most importantly, not re-installing any dependencies already provided by rocker.
